Supplementary Information for:

### 2017-02-07 JTB_supp/JTB_supp.Rmd
turn on eval to run on remote server

# Figure S3 
```{r sens_ILHN, cache=T, echo=F, eval=F, fig.cap="**Fig. S3. Sensitivity analysis under high DIN (4e-6 M) and intermediate light (15 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S4 
```{r sens_LLLN, cache=T, echo=F, eval=F, fig.cap="**Sensitivity analysis under low DIN (1e-7 M) and low light (2 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S5
```{r sens_LLHN, cache=T, echo=F, eval=F, fig.cap="**Fig. S5. Sensitivity analysis under high DIN (4e-6 M) and low light (2 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S6
```{r sens_HLLN, cache=T, echo=F, eval=F, fig.cap="**Fig. S6. Sensitivity analysis under low DIN (1e-7 M) and high light (25 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S7
```{r sens_HLHN, cache=T, echo=F, eval=F, fig.cap="Fig. S7. Sensitivity analysis under high DIN (4e-6 M) and high light (25 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S8
```{r FigS8, cache=T, fig.width=7, fig.height=7, echo=F, eval=F, fig.cap="**Fig. S8. Full system dynamics of seasonal light variation at two nutrient levels.** This figure accompanies Figure 5 in the main text, and shows additional model fluxes that demonstrate the mechanisms underlying the changes in the system state in these simulations."}
# Set parameters
defpars <- def_pars()  # Get default parameters

@@

# Figure S9
```{r runFigS9, cache=T, include=F, eval=F}
# Set up cluster for parallel processing
cl <- makeCluster(detectCores())  # Initiate cluster
registerDoParallel(cl)

@@

```{r plotFigS9, cache=T, fig.width=7, fig.height=7, echo=F, message=F, eval=F, fig.cap="**Fig. S9. Hysteresis under different nutrient and feeding regimes.** This figure accompanies Fig. 2 in the main text. These figures show steady state S:H biomass ratios in constant environments with varying DIN and food (X) levels, with initial S:H biomass values of either 0.1 or 0.0001. Points are colored according to whether the host exhibits positive (black) or negative (red) growth at steady state."}
# Create plot
par(mfrow=c(2,2), mar=c(3,3,1,1), mgp=c(1.5,0.5,0), tcl=-0.025)

>>>>

# Figure S3 
```{r sens_ILHN, cache=T, echo=F, eval=T, fig.cap="**Fig. S3. Sensitivity analysis under high DIN (4e-6 M) and intermediate light (15 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S4 
```{r sens_LLLN, cache=T, echo=F, eval=T, fig.cap="**Sensitivity analysis under low DIN (1e-7 M) and low light (2 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S5
```{r sens_LLHN, cache=T, echo=F, eval=T, fig.cap="**Fig. S5. Sensitivity analysis under high DIN (4e-6 M) and low light (2 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S6
```{r sens_HLLN, cache=T, echo=F, eval=T, fig.cap="**Fig. S6. Sensitivity analysis under low DIN (1e-7 M) and high light (25 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S7
```{r sens_HLHN, cache=T, echo=F, eval=T, fig.cap="Fig. S7. Sensitivity analysis under high DIN (4e-6 M) and high light (25 mol m^-2^ d^-1^).** See Fig. 4 in main text."}
# Set up time vector and parameters
defpars <- def_pars()  # Get default parameters
defpars <- replace(defpars, "initS", 1)  # Start with high S biomass to avoid alternate steady state of negative growth

@@

# Figure S8
```{r FigS8, cache=T, fig.width=7, fig.height=7, echo=F, eval=T, fig.cap="**Fig. S8. Full system dynamics of seasonal light variation at two nutrient levels.** This figure accompanies Figure 5 in the main text, and shows additional model fluxes that demonstrate the mechanisms underlying the changes in the system state in these simulations."}
# Set parameters
defpars <- def_pars()  # Get default parameters

@@

# Figure S9
```{r runFigS9, cache=T, include=F, eval=T}
# Set up cluster for parallel processing
cl <- makeCluster(detectCores())  # Initiate cluster
registerDoParallel(cl)

@@

```{r plotFigS9, cache=T, fig.width=7, fig.height=7, echo=F, message=F, eval=T, fig.cap="**Fig. S9. Hysteresis under different nutrient and feeding regimes.** This figure accompanies Fig. 2 in the main text. These figures show steady state S:H biomass ratios in constant environments with varying DIN and food (X) levels, with initial S:H biomass values of either 0.1 or 0.0001. Points are colored according to whether the host exhibits positive (black) or negative (red) growth at steady state."}
# Create plot
par(mfrow=c(2,2), mar=c(3,3,1,1), mgp=c(1.5,0.5,0), tcl=-0.025)
